% Section 6 -- Discussion and Limitations. Pages target ~0.6.
% Required by venue: explicit Limitations subsection.
\section{Discussion and Limitations}
\label{sec:discussion}

\subsection{When this framework is the wrong choice}
\label{sec:discussion-wrong-choice}

\texttt{cursor\_manager} is designed for a specific regime: revising
and shipping multi-page conference papers under hard discipline, with
a human in the loop for strategic decisions. Four regimes are wrong
choices. \textbf{(W1) From-scratch authoring.} The writing-only scope
provides no value when there is no v1 draft; the paper must come from
an end-to-end system such as \citet{song2026paperorchestra} or
\citet{sibyl2026system}. \textbf{(W2) Experiment iteration.} We have
no experiment-runner sub-agent and explicitly delegate GPU scheduling
to the human; for that regime use \citet{sibyl2026system} or
\citet{karpathy2026autoresearch}. \textbf{(W3) Throughput at
borderline-reject quality.} The right tool for FARS-style 100-paper
deployments at mean score 5.05 \citep{fars2026analemma} is FARS, not
us; our per-commit discipline overhead is sensible only when the goal
is a single paper at $\geq 6$ on a primary track. \textbf{(W4)
Fully-autonomous operation.} The \texttt{[BLOCKED-DECISION]} protocol
is unusable by construction; removing the halt would defeat it. We
argue in \S\ref{sec:limitations} that fully-autonomous operation is
in any case incompatible with current primary-track submission
requirements, so this case is largely hypothetical.

\subsection{Limitations}
\label{sec:limitations}

We list four scope limitations and refer the reader to
Appendix~\ref{app:limitations} for the full six. \textbf{(L1)}
\texttt{cursor\_manager} edits text but cannot author or update
figures (PaperOrchestra's Plot agent \citep{song2026paperorchestra}
is a natural complement). \textbf{(L2)} The system reads experiment
results computed elsewhere but does not allocate GPUs or schedule
jobs (Sibyl \citep{sibyl2026system} does). \textbf{(L3)} The
cross-model ablation in \S\ref{sec:case-ablation} uses single-digit
injected violations per condition and is not statistically powered
for fine distinctions. \textbf{(L4)} A single dogfood deployment,
however carefully audited, does not settle whether the discipline
mechanisms transfer to other groups, paper styles, or LLM backends.

\paragraph{Closing remark.}
When inference token budgets are no longer binding, the interesting
variable is \emph{discipline}: the contract between an autonomous
writing agent and the human operator that prevents the agent's free
parameters from drifting through the parts of the paper that
constitute its claims. \texttt{cursor\_manager}'s four discipline
mechanisms target the four failure modes separating benchmark-grade
from submission-grade output. The system, the sub-agent contract,
this paper's source, and the public MIT release in Appendix~\ref{app:repo}
make the engineering artefacts reproducible (git-history split described
there).
\label{sec:conclusion}
